Beyond clines: lineages and haplotype blocks in hybrid zones

### 2016-04-26 drafts/supplement.tex
fixing up the supplement

\begin{figure}
    \includegraphics{{figs/alleleFrequencies_sim_s0.01_tau100_closely_linked}.pdf}
    \caption{
    Frequency of ancestry $B$,
    across geography at different physical positions on the genome, simulated for a hybrid zone
     $T=100$ generations after secondary contact, with $s=0.1$,
     using 50 demes, each with 500 diploid individuals and $\sigma=1$.
    Each line represents a locus some distance $r$ away from the true target of selection with colors corresponding to different values of $r$, transitioning from red (tight linkage to selected site) to blue (distantly linked).
    Grey lines represent the same positions from a simulation with
    identical parameters except that $s=0$. 
    Corresponding theoretical quantities are shown juxtaposed in Figure \ref{fig:alleleFreq_tau100_comparison};
    the same plot is shown with weaker selection in Figure \ref{alleleFreq_tau100_weaker_s} and at a longer time in Figure \ref{alleleFreq_tau1000}.
}\label{alleleFreq_tau100}
\end{figure}

@@

\begin{figure}
\includegraphics{figs/ratioAdjacentBlocksAlongChromAncBConditioning.pdf}
    \caption{The statistic $\bar C(m,x)$: the ratio $\frac{2\sum{l_B(m_i)}}{\sum{l_A(m_i-)+I_A(m_i+)}}$ of mean block length and mean adjacent block lengths across a simulated chromosome with a single underdominant site and conditioning on ancestry $B$ at the selected site ($s=0.01, T=1000$).  Each line represents a deme and is normalized by mean block length across the chromosome in the deme.}\label{Supp:ratioBlockAdjacent}
\end{figure}

>>>>

\begin{figure}
    \includegraphics{figs/alleleFrequencies_sim.pdf}
    \caption{
    Frequency of ancestry $B$,
    across geography at different physical positions on the genome, simulated for a hybrid zone
     $T=100$ generations after secondary contact, with $s=0.1$,
     using 50 demes, each with 500 diploid individuals and $\sigma=1$.
    Each line represents a locus some distance $r$ away from the true target of selection with colors corresponding to different values of $r$, transitioning from red (tight linkage to selected site) to blue (distantly linked).
    Grey lines represent the same positions from a simulation with
    identical parameters except that $s=0$. 
    Corresponding theoretical quantities are shown juxtaposed in Figure \ref{fig:alleleFreq_tau100_comparison};
    the same plot is shown with weaker selection in Figure \ref{alleleFreq_tau100_weaker_s} and at a longer time in Figure \ref{alleleFreq_tau1000}.
}\label{alleleFreq_tau100}
\end{figure}

@@

\begin{figure}
\includegraphics{figs/s0point01_ratioAdjacentBlocksAlongChromAncBConditioningHighRes.pdf}
    \caption{The statistic $\bar C(m,x)$: the ratio $\frac{2\sum{l_B(m_i)}}{\sum{l_A(m_i-)+I_A(m_i+)}}$ of mean block length and mean adjacent block lengths across a simulated chromosome with a single underdominant site and conditioning on ancestry $B$ at the selected site ($s=0.01, T=1000$).  Each line represents a deme and is normalized by mean block length across the chromosome in the deme. This  simulation corresponds to that represented in Figure~\ref{Fig:blockLengthsZoom}; note the difference in y-axis scale.}\label{Supp:ratioBlockAdjacent}
\end{figure}
